Full-core analysis of thorium-fueled Molten Salt Breeder Reactor using the SERPENT 2 Monte Carlo code

### 2017-08-31 introduction.tex
shortened page to 4

\section{Abstract}
The French 2012-2015 Commission Nationale d'Evaluation reports
\cite{noauthor_cne2_nodate} emphasize preparation for a transition from \glspl{LWR} to \glspl{SFR}.
This paper uses \Cyclus to explore the feasibility of using \gls{UNF} from other EU nations
for French transition into a \gls{SFR} fleet without additional construction of \glspl{LWR}.
A \Cyclus simulation ran from 1950 to 2160 for EU to track the \gls{UNF} mass
and tails inventory to support
the transition into \glspl{SFR} (66GWe - 110 \glspl{SFR}). The study concludes that France can avoid deployment
of additional \glspl{LWR} by accepting \gls{UNF} from other EU nations.

@@

The nuclear history of EU nations are modeled, using the \gls{PRIS} open-source 
database from \gls{IAEA}. That database is imported as a csv file, to populate the simulation
with deployment information, listing the country, reactor unit, type, net capacity (MWe), status,
operator, construction date, first criticality date, first grid date, commercial date, shutdown
date (if applicable), and unit capacity factor for 2013. Then only the \gls{EU} countries are extracted
from the csv file. A python script is written up to generate a \Cyclus input file from the csv file,
which lists the individual reactor units as agents. After running the \Cyclus input file,
another python script analyzes the output file. All the scripts and data used
in this paper are available in \cite{jin_whan_bae_2017_854820}.
%% Probably a separate repository is needed..?

>>>>

\section{Abstract}
The French 2012-2015 Commission Nationale d'Evaluation reports
\cite{noauthor_reports_2015} emphasize preparation for a transition from \glspl{LWR} to \glspl{SFR}.
This paper uses \Cyclus to explore the feasibility of using \gls{UNF} from other EU nations
for French transition into a \gls{SFR} fleet without additional construction of \glspl{LWR}.
A \Cyclus simulation ran from 1950 to 2160 for EU to track the \gls{UNF} mass
and tails inventory to support
the transition into \glspl{SFR} (66GWe - 110 \glspl{SFR}). The study concludes that France can avoid deployment
of additional \glspl{LWR} by accepting \gls{UNF} from other EU nations.

@@

The nuclear history of EU nations are modeled, using the \gls{PRIS} open-source 
database from \gls{IAEA}. That database is imported as a csv file, to populate the simulation
with deployment information, listing the country, reactor unit, type, net capacity (MWe), status,
operator, construction date, first criticality date, first grid date, commercial date, shutdown
date (if applicable), and unit capacity factor for 2013. Then only the \gls{EU} countries are extracted
from the csv file. A python script is written up to generate a \Cyclus input file from the csv file,
which lists the individual reactor units as agents. After running the \Cyclus input file,
another python script analyzes the output file. All the scripts and data used
in this paper are available in \cite{bae_arfc/transition-scenarios:_2017}.
%% Probably a separate repository is needed..?

### 2017-08-31 results.tex
shortened page to 4

@@

\begin{table}[h]
	\centering
		\scalebox{0.77}{
	\begin{tabular}{|c|c|c|c|}
		\hline
		Category & Unit & Value & Specifics\\ \hline
		Total UOX Usage & MTHM & 181,471 &  \\ \hline
		Total MOX Usage & MTHM & 6,302 & \\ \hline
		Total Used UOX Stored & MTHM & 141,659 & \gls{UNF} that is not reprocessed\\ \hline
		Total Used  MOX Stored & MTHM & 3,611 & \gls{UNF} that is not reprocessed \\ \hline
		Total Tailings & MTHM & 1,081,826 & \\ \hline
		Total Natural U Used & MTHM & 1,269,897 & \\ \hline
	\end{tabular}
}
	\caption{Simulation Results for Historical Nuclear Operation of \gls{EU} Nations}
	\label{tab:sim_result}
	\end {table}
	\FloatBarrier

	Figures \ref{fig:eu_tail} and \ref{fig:eu_snf} show the 
	timeseries of mass of tailings and used fuel accumulation in \gls{EU}.
	Figure \ref{fig:eu_fuel} shows the amount of fuel used in \gls{EU}.

@@

	From Varaine et al. \cite{marsaultmarie-sophie_pre-conceptual_2012}, a French
	ASTRID-type \gls{SFR} of capacity 600 MWe needs $1.225$ tons of
	plutonium a year, with an initial plutonium loading of $4.9$ tons. 
	Thus, the number of \glspl{SFR} that can be loaded with the reprocessed
	plutonium from \gls{UNF} can be estimated to $\frac{Pu \ from \ legacy \ \gls{UNF}}{4.9} \approx 270$ \glspl{SFR},
	assuming infinite reprocessing and fabrication capacity as well as
	abundant depleted uranium supply.

@@

	\Cref{fig:fuel} shows \gls{MOX} loaded in the \glspl{SFR} per month.
	The spikes are due to initial fuel demand for new deployment of \glspl{SFR}.
	The initial loading of new \glspl{SFR} are done with the \gls{MOX} created
	from legacy \gls{UNF}. Once there are enough amounts of extra plutonium creation
	by deployed \glspl{SFR}, the legacy \gls{UNF} is no longer used.

@@

	\Cref{fig:reprocess_waste} shows the amount of reprocessing waste
	(minor actinides, fission products) over time. The spikes in the 
	waste discharge is due to large influx of spent fuel from
	decommissioned \glspl{SFR}.\Cref{fig:pu_no_cum} shows the separated plutonium discharge
	per month from the reprocessing plant. The plutonium outflux
	does not precisely follow the fuel demand because \Cyclus agents have
	material buffers that store commodity fuel for later usage. 
	\Cref{tab:sfr_sim_result} lists metrics obtained from the second simulation.

@@

	\begin{figure}[htbp!]
		\begin{center}
			\includegraphics[width=\columnwidth]{./images/french-transition/reprocess_waste.png}
		\end{center}
		\caption{Reprocessing waste discharge from Reprocessing Plant}
		\label{fig:reprocess_waste}
	\end{figure}

	\begin{table}[h]
		\centering
		\scalebox{0.86}{
			\begin{tabular}{|c|c|c|}
				\hline
				Category & Unit & Value  \\ \hline
				Total MOX used & MTHM & 127,640  \\ \hline
				Total \glspl{SFR} Deployed & & 220 \\ \hline
				Total Plutonium Reprocessed & MTHM & 16,352 \\ \hline
				Total MOX from UOX Waste & MTHM & 6,570  \\ \hline
				Total MOX from MOX Waste & MTHM  & 121,070 \\ \hline
				Total Tails used & MTHM & 116,153 \\ \hline
				Total legacy UNF reprocessed & MTHM & 77,082 \\ \hline
				Total Reprocessed Uranium Stockpile & MTHM & 184,172 \\ \hline
				Total Reprocess Waste & MTHM & 16,352 \\ \hline
			\end{tabular}}
			\caption {\gls{SFR} Simulation Results}
			\label{tab:sfr_sim_result}
			\end {table}

>>>>

\begin{table}[h]
	\centering
	\scalebox{0.77}{
		\begin{tabular}{|c|c|c|c|}
			\hline
			Category & Unit & Value & Specifics\\ \hline
			Total UOX Usage & MTHM & 181,471 &  \\ \hline
			Total MOX Usage & MTHM & 6,302 & \\ \hline
			Total Used UOX Stored & MTHM & 141,659 & \gls{UNF} that is not reprocessed\\ \hline
			Total Used  MOX Stored & MTHM & 3,611 & \gls{UNF} that is not reprocessed \\ \hline
			Total Tailings & MTHM & 1,081,826 & \\ \hline
			Total Natural U Used & MTHM & 1,269,897 & \\ \hline
		\end{tabular}

@@

}
	\caption{Simulation Results for Historical Nuclear Operation of \gls{EU} Nations}
	\label{tab:sim_result}
	\end {table}
	Figures \ref{fig:eu_tail} and \ref{fig:eu_snf} show the 
	timeseries of mass of tailings and used fuel accumulation in \gls{EU}.
	Figure \ref{fig:eu_fuel} shows the amount of fuel used in \gls{EU}.

@@

	From Varaine et al. \cite{varaine_pre-conceptual_2012}, a French
	ASTRID-type \gls{SFR} of capacity 600 MWe needs $1.225$ tons of
	plutonium a year, with an initial plutonium loading of $4.9$ tons. 
	Thus, the number of \glspl{SFR} that can be loaded with the reprocessed
	plutonium from \gls{UNF} can be estimated to 270 \glspl{SFR},
	assuming infinite reprocessing and fabrication capacity as well as
	abundant depleted uranium supply.

@@

@@

@@

	\Cref{fig:fuel} shows \gls{MOX} loaded in the \glspl{SFR} per month.
	The spikes are due to initial fuel demand for new deployment of \glspl{SFR}.
	The initial loading of new \glspl{SFR} are done with the \gls{MOX} created
	from legacy \gls{UNF}. Once there are enough amounts of extra plutonium creation
	by deployed \glspl{SFR}, the legacy \gls{UNF} is no longer used. 
	\begin{table}[h]
		\centering
		\scalebox{0.86}{
			\begin{tabular}{|c|c|c|}
				\hline
				Category & Unit & Value  \\ \hline
				Total MOX used & MTHM & 127,640  \\ \hline
				Total \glspl{SFR} Deployed & & 220 \\ \hline
				Total Plutonium Reprocessed & MTHM & 16,352 \\ \hline
				Total MOX from UOX Waste & MTHM & 6,570  \\ \hline
				Total MOX from MOX Waste & MTHM  & 121,070 \\ \hline
				Total Tails used & MTHM & 116,153 \\ \hline
				Total legacy UNF reprocessed & MTHM & 77,082 \\ \hline
				Total Reprocessed Uranium Stockpile & MTHM & 184,172 \\ \hline
				Total Reprocess Waste & MTHM & 16,352 \\ \hline
			\end{tabular}}
			\caption {\gls{SFR} Simulation Results}
			\label{tab:sfr_sim_result}
			\end {table}

	\Cref{fig:pu_no_cum} shows the separated plutonium discharge
	per month from the reprocessing plant. The plutonium outflux
	does not precisely follow the fuel demand because \Cyclus agents have
	material buffers that store commodity fuel for later usage. 
	\Cref{tab:sfr_sim_result} lists metrics obtained from the second simulation.
